From centralized certification systems to more internet-like ones

### 2015-12-26 paper.tex
Sovereign keys -> DONE !

Sovereign keys are an Electric Frontier Foundation (EFF) proposition.

@@

>>>>

Sovereign keys are an Electric Frontier Foundation (EFF\footnote{www.eff.org}) proposition.

@@

A sovereign key has a cycle of life than begins with the generation of a cryptographic pair of keys	by the domain administrator (who wants to use TLS server on his domain). This administrtor must at first, proove that he really is controlling his domain before seeing it in public data-structures.\\
To do so, he must give his certificate (which the CN covers his domain name declared protected by the sovereign key) signed by an AC recognized by the \textit{timeline servers}\footnote{The list of AC's recognized by the timeline servers is public and must be up to date, by conception.} or through DANE (once the norm will by published and implemented).\\
During the public key registering by the timeline servers, proofs of control on the domain are examined and added to the sovereign key metadata. Other informations are added sch as:
\begin{itemize}
	\item Expiration date.
	\item Names (and ports) of TLS services uses and protected by the sovereign key.
	\item A list (that may be empty) of domain names which their sovereign keys are granted to revok (in case of loose of control of the private part of the sovereign key) the entry being entered.
\end{itemize}
A data-structure of sovereign keys being a append-only list, once the sovereign key is entered, it cannot be removed. The domain administrator can only modify informations by pushing informations in that data-structure. To remove a sovereign key (in the case of losing the private key), the domain adminstrator need to use a domain name with a sovereign key granted to modify its own sovereign key (thus present in the list of his own sovereign key, see in the item list below) or wait for his sovereign key expiration date.

This structure is useful because it protects from DNS or AC compromise of sovereign key by smurf attacks\footnote{Attacker able to give proof of domain control.}. It also need to be used with care, because an unadvise administrator may lose control of its own domain.\\

The dark points of this systems are:
\begin{itemize}
	\item A service declared protected in a data-structure of a timeline server need to use a secure protocol (HTTPS instead of HTTP for example) to avoid downgrade attacks. It may be seen as an intrusion into the freedom of a service governance.
	\item From loosing a private key may result a long term denial of service if no domain sovereign key is granted to modify the private key's sovereign key.
	\item A compromized private key may lead to a total loose of control of the entire domain.
	\item The use of ACs to certify the domain owner is the big problem of this system.
\end{itemize}
